Appendix A

### 2020-10-05 appendixA/appendixA.Rmd
Individual level is ready, but gt table not showing in the html.

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE, results = 'hide')
```

```{r}
library(aracari)
library(dplyr)
library(ggplot2)
library(tidyr)
library(purrr)
library(stringr)
library(fitdistrplus)
library(cowplot)
library(RColorBrewer)

@@

@@

prms.df %>% 
  mutate(param = str_to_upper(param), 
         dist = str_replace(dist, "exp", "Exponential"),
         dist = str_replace(dist, "gamma", "Gamma"),
         dist = str_replace(dist, "weibull", "Weibull"),
         dist = str_replace(dist, "lnorm", "Lognormal"),
         data = str_replace(data, "pop", "POP")) %>% 
  mutate(kpars = ifelse(dist == "Exponential", 1, 2),
         BIC = log(n)*kpars - 2*loglik,
         AIC = 2*kpars - 2*loglik,
         AICc = AIC + (2* kpars * (kpars+1)/(n-kpars-1))) %>% 
  group_by(data) %>% 
  mutate(deltaBIC = signif(BIC - min(BIC), 3),
         deltaAIC = signif(AIC - min(AIC), 3),
         deltaAICc = signif(AICc - min(AICc), 3)) %>% 
  mutate(best_col = ifelse(deltaBIC == 0, "#ffaa00", "black"))-> nice_prms

@@

```{r}
nice_prms %>%
  dplyr::select(., dist, data, deltaBIC, deltaAIC, deltaAICc) %>% 
  distinct() %>% 
  pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
  ggplot(., aes(x = ic, y = value, color = dist)) +
  geom_point() +
  facet_wrap(~data, scales = "free")
```

```{r}
prms.df %>% 
  filter(., data != "pop") %>%
  dplyr::select(., loglik, n, dist) %>% 
  distinct() %>%
  mutate(kpars = ifelse(dist == "exp", 1, 2)) %>% 
  group_by(dist) %>% 
  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik), 
            AIC = 2*(sum(kpars)) - 2*(sum(loglik)),
            AICc = 2*(sum(kpars)) - 2*(sum(loglik)) + (2* sum(kpars) * (sum(kpars)+1)/(sum(n)-sum(kpars)-1))) %>%
    mutate(deltaAIC = signif(AIC - min(AIC), 3),
         deltaAICc = signif(AICc - min(AICc), 3),
         deltaBIC = signif(BIC - min(BIC), 3),
         data = "ind") %>% 
  full_join(., popind.IC %>% 
  filter(., data == "pop")) -> popind.IC.comp

```{r}
popind.IC.comp %>% 
  pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
  ggplot(., aes(x = ic, y = value, color = dist)) +
  geom_point() +
  facet_wrap(~data, scales = "free")
```

# Get the multi-distribution model fit
popind.IC %>% 
  dplyr::filter(., data != "pop" & deltaBIC == 0) %>% 
  ungroup() %>% 
  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik)) %>% 
  as.numeric() -> multi.BIC

popind.IC %>% 
  dplyr::filter(., data != "pop" & deltaAIC == 0) %>% 
  ungroup() %>% 
  summarise(AIC = 2*(sum(kpars)) - 2*(sum(loglik))) %>% 
  as.numeric() -> multi.AIC

popind.IC %>% 
  dplyr::filter(., data != "pop" & deltaAICc == 0) %>% 
  ungroup() %>% 
  summarise(AICc = 2*(sum(kpars)) - 2*(sum(loglik)) + (2* sum(kpars) * (sum(kpars)+1)/(sum(n)-sum(kpars)-1))) %>% 
  as.numeric()-> multi.AICc

popind.IC.comp %>% 
  dplyr::select(., dist, BIC, AIC, AICc, data) %>% 
  bind_rows(., data.frame(dist = "multi", BIC = multi.BIC, AIC = multi.AIC, AICc = multi.AICc, data = "multi")) %>%
  pivot_longer(., cols = starts_with(c("BIC", "AIC")), names_to = "ic", values_to = "value") %>% 
  ggplot(., aes(x = dist, y = value, color = data)) +
  geom_point() +
  facet_wrap(~ic, scales = "free") +
  theme(axis.text.x = element_text(angle = 90))

@@

```{r}
# Save parameters

>>>>

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
```

```{r}
library(aracari)
library(dplyr)
library(ggplot2)
library(tidyr)
library(purrr)
library(stringr)
library(fitdistrplus)
library(cowplot)
library(RColorBrewer)
library(gt)

@@

```{r}
prms.df %>% 
  mutate(param = str_to_upper(param), 
         dist = str_replace(dist, "exp", "Exponential"),
         dist = str_replace(dist, "gamma", "Gamma"),
         dist = str_replace(dist, "weibull", "Weibull"),
         dist = str_replace(dist, "lnorm", "Lognormal"),
         data = str_replace(data, "pop", "POP")) %>% 
  mutate(kpars = ifelse(dist == "Exponential", 1, 2),
         BIC = log(n)*kpars - 2*loglik,
         AIC = 2*kpars - 2*loglik,
         AICc = AIC + (2* kpars * (kpars+1)/(n-kpars-1))) %>% 
  group_by(data) %>% 
  mutate(deltaBIC = signif(BIC - min(BIC), 3),
         deltaAIC = signif(AIC - min(AIC), 3),
         deltaAICc = signif(AICc - min(AICc), 3)) %>% 
  mutate(best_col = ifelse(deltaBIC == 0, "#ffaa00", "black"))-> nice_prms
```

The three information criteria differ in their model choices, with AIC and corrected AIC (AICc) selecting the same models, and BIC selecting different ones.

```{r fig.width=12, fig.height=4}
# To visualize the differences in the information criteria at the individual level

nice_prms %>% 
  dplyr::select(dist, data, deltaAIC, deltaAICc, deltaBIC) %>% 
  distinct() %>% 
  pivot_longer(., cols = starts_with("delta"), names_to = "ic", values_to = "value") %>% 
  mutate(plot_alpha = ifelse(value == "0", 1, 0.8)) %>% 
  ggplot(., aes(x = data, y = value, color = dist 
                #alpha = plot_alpha
                )) +
  facet_wrap(~ic) +
  geom_point(size = 3) +
  scale_color_brewer(palette = "Spectral") + 
  #scale_alpha_continuous(range = c(0.5, 1)) +
  labs(x = "") +
  theme(legend.position = "bottom",
        axis.text.x = element_text(color = c(rep("black", 12), "red"))) +
  guides(color = guide_legend(title = "Distribution"))

# Create the dataframe that compares the models by information criteria
nice_prms %>% 
  filter(., data != "POP") %>%
  dplyr::select(., loglik, n, dist) %>% 
  distinct() %>%
  mutate(kpars = ifelse(dist == "Exponential", 1, 2)) %>% 
  group_by(dist) %>% 
  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik), 
            AIC = 2*(sum(kpars)) - 2*(sum(loglik)),
            AICc = 2*(sum(kpars)) - 2*(sum(loglik)) + (2* sum(kpars) * (sum(kpars)+1)/(sum(n)-sum(kpars)-1))) %>%
    mutate(deltaAIC = signif(AIC - min(AIC), 3),
         deltaAICc = signif(AICc - min(AICc), 3),
         deltaBIC = signif(BIC - min(BIC), 3),
         data = "Individual") %>% 
  full_join(., nice_prms %>%
              filter(., data == "POP") %>% 
              dplyr::select(dist, BIC, AIC, AICc, deltaAIC, deltaAICc, deltaBIC) %>% 
              distinct() %>% 
              mutate(data = "Population")) -> popind.IC.comp

# Get the multi-distribution model fit
nice_prms %>% 
  dplyr::select(., dist, data, loglik, n, kpars, deltaBIC) %>% 
  dplyr::filter(., data != "POP" & deltaBIC == 0) %>% 
  distinct() %>% 
  ungroup() %>% 
  summarise(BIC = log(sum(n))*sum(kpars) - 2 * sum(loglik)) %>% 
  as.numeric() -> multi.BIC

nice_prms %>% 
  dplyr::select(., dist, data, loglik, n, kpars, deltaAIC) %>% 
  dplyr::filter(., data != "POP" & deltaAIC == 0) %>% 
  distinct() %>%
  ungroup() %>% 
  summarise(AIC = 2*(sum(kpars)) - 2*(sum(loglik))) %>% 
  as.numeric() -> multi.AIC

nice_prms %>% 
  dplyr::select(., dist, data, loglik, n, kpars, deltaAICc) %>% 
  dplyr::filter(., data != "POP" & deltaAICc == 0) %>% 
  distinct() %>%
  ungroup() %>% 
  summarise(AICc = 2*(sum(kpars)) - 2*(sum(loglik)) + (2* sum(kpars) * (sum(kpars)+1)/(sum(n)-sum(kpars)-1))) %>% 
  as.numeric()-> multi.AICc

popind.IC.comp %>% 
  dplyr::select(., dist, BIC, AIC, AICc, data) %>% 
  bind_rows(., data.frame(dist = "Multidist", BIC = multi.BIC, AIC = multi.AIC, AICc = multi.AICc, data = "Multidist")) -> model_comp_IC

```{r}
# Table for BIC only

model_comp_IC %>% 
  dplyr::select(data, dist, BIC) %>% 
  group_by(data) %>% 
  mutate(delta_within = signif(BIC - min(BIC), digits = 2)) %>% 
  ungroup() %>% 
  mutate(delta_across = signif(BIC - min(BIC), digits = 2)) %>% 
  dplyr::select(., -data)-> data_gt

gt_tbl <- gt(data_gt, rowname_col = "dist")

gt_tbl %>% 
  tab_header(
    title = md("**BIC comparisons across levels**")
  ) %>% 
  tab_stubhead(label = "Model") %>% 
  tab_row_group(
    group = "Multidist",
    rows = 9
  ) %>% 
  tab_row_group(
    group = "Individual",
    rows = 1:4
  ) %>% 
  tab_row_group(
    group = "Population", 
    rows = 5:8
  ) %>% 
  cols_label(
    delta_within = html("&Delta; BIC<sub>within</sub>"),
    delta_across = html("&Delta; BIC<sub>across</sub>")
  )

@@

@@

@@

```{r eval = FALSE}
# Save parameters
